Globally-centered autocovariances in MCMC

### 2020-09-02 Paper/main.tex
zzzzz (done with the appendix)

Conditions for strong consistency of $\hat{\Sigma}_s$ for polynomially ergodic Markov chains are in \cite{vats:fleg:jon:2018}. Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.

Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}. However, \cite{hannan:1970} proved the results assuming $\mu_g$ was known. Here, we present the results under mild conditions for when $\mu_g$ is replaced by $\bar{\bar{Y}}$. Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, respectively.

\begin{theorem}\label{th:G-SVE_bias}
Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that 
\[
\lim _{x \to 0} \dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty
\] 
and $b_n^q/n \to 0$ as $n \to \infty$. Then $ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.$
% \[
%  \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.
%  \]
\end{theorem}

@@

Finally, we will solve for $P_2$. Note that $O_1 = (\abs{k}/n)\mathcal{O}(1/n)$ and $O_2 = \mathcal{O}(1/n)$. So,
  \begin{align*}
    P_2  & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{k}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{1}{n}\right) \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{1}{n}\right) = o\left(\dfrac{1}{b_n^q}\right) \,.
 \end{align*}

%
Using \eqref{eq:P1_decomp},\eqref{eq:P1_first}, \eqref{eq:P1_second}, and \eqref{eq:P1_third} in \eqref{eq:bias_gsve},
\[
\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
\]
which completes the result.
%
 % We have shown that all, but one, terms are $o(1/b_n^q)$. Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms. This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu_g$ in our replicated autovariance estimator. Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu_g$ contributes only $o(1)$ terms. 
% \end{proof}

@@

 Due to the strong consistency proof from Theorem \ref{th:consistency}, as $n \to \infty$,
\label{eq:G-SVE_asv_consis}
 \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
We have shown from the proof of strong consistency that,

@@

where it has been shown already that $g_1(n), g_2(n), g_3(n) \to 0$ as $n \to \infty$. By \eqref{eq:G-SVE_asv_consis}, there exists an $N_0$ such that

@@

\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]

@@

\cite{hannan:1970} has given the calculations for variance of $\tilde{\Sigma}$ as 
\begin{equation} \label{eq:hannan_var}
\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = \left[\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right) \right]\int_{-\infty}^{\infty}w^2(x)dx + o(1)    
\end{equation}
Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{G}$ gives the result of the theorem.

>>>>

Conditions for strong consistency of $\hat{\Sigma}_s$ for polynomially ergodic Markov chains are in \cite{vats:fleg:jon:2018}. Typically, $b_n = \lfloor n^{\nu} \rfloor$ for some $0< \nu <1$ for which $n^{-1} b_n \log \log n \to 0$, thus Theorem~\ref{th:consistency} presents no added conditions for strong consistency.Our next two results establish large-sample bias and variance for G-SV and mimic those of $\hat{\Sigma}_s$ which can be found in \cite{hannan:1970}. Let $\Sigma^{ij}$ and $\hat{\Sigma}_G^{ij}$ denote the $ij$th element of the matrix $\Sigma$ and $\hat{\Sigma}_G$, respectively.

\begin{theorem}\label{th:G-SVE_bias}
Let the assumptions of Theorem~\ref{thm:kuelbs} hold with $q$ such that 
\[
\lim _{x \to 0} \dfrac{1 - w(x)}{\abs{x}^q} = k_q < \infty\,
\] 
and $b_n^{q+1}/n \to 0$ as $n \to \infty$. Then $ \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.$
% \[
%  \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}\,.
%  \]
\end{theorem}
\cite{hannan:1970} proved a similar bias result assuming $\mu_g$ was known with the rate $b_n^q/n \to 0$ as $n \to \infty$. Similar to \cite{ande:1971} for the univariate case, in Theorem~\ref{th:G-SVE_bias}, we require $b_n^{q+1}/n \to 0$ as $n\to \infty$ for the multivariate case for when $\mu_g$ is replaced by $\bar{\bar{Y}}$.

@@

Finally, we will solve for $P_2$. Note that $O_1 = (\abs{k}/n)\mathcal{O}(1/n)$ and $O_2 = \mathcal{O}(1/n)$. So,
  \begin{align*}
    P_2  & \leq \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_1} + \sum_{k=-n+1}^{n-1}\abs{w\left(\dfrac{k}{b_n}\right)O_2} \\
      &= \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-n+1}^{n-1}\dfrac{\abs{k}}{n}\abs{w\left(\dfrac{k}{b_n}\right)} + \mathcal{O}\left(\dfrac{1}{n}\right)\sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{b_n}{n}\right)\dfrac{1}{b_n} \sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\\
      &= \mathcal{O}\left(\dfrac{b_n}{n}\right) = o\left(\dfrac{b_n}{b_n^{q+1}}\right) = o\left(\dfrac{1}{b_n^{q}}\right) \,. \numberthis \label{eq:P_2}
 \end{align*}

%
Using \eqref{eq:P1_decomp},\eqref{eq:P1_first}, \eqref{eq:P1_second}, \eqref{eq:P1_third}, and \eqref{eq:P_2} in \eqref{eq:bias_gsve},
\[
\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -\dfrac{k_q \Phi^{(q)} }{b_n^q} + o\left( \dfrac{1}{b_n^q} \right)\,,
\]
which completes the result.
%
 % We have shown that all, but one, terms are $o(1/b_n^q)$. Therefore, the limiting value of $b_n^q\mathbb{E}[\hat{\Sigma}_{G-} - \Sigma]$ is proved to be same as that of $b_n^q\mathbb{E}[\tilde{\Sigma} - \Sigma]$ in \cite{hannan2009multiple} with some extra $o(1)$ terms. This is quite intuitive as we are using a strongly consistent estimator $\bar{\bar{X}}$ for $\mu_g$ in our replicated autovariance estimator. Similar to theorem \ref{th:G-_expec}, the effect of estimating $\mu_g$ contributes only $o(1)$ terms. 
% \end{proof}

@@

%  Due to the strong consistency proof from Theorem \ref{th:consistency}, as $n \to \infty$,
% \begin{equation}
% \label{eq:G-SVE_asv_consis}
%  \left|\hat{\Sigma}_{G} -  \tilde{\Sigma}\right| \to 0 \text{ with probability 1}\,. 
% We have shown from the proof of strong consistency that,
By Lemma~\ref{lemma:G-SVE_breakdown},

@@

where $g_1(n), g_2(n), g_3(n) \to 0$ as $n \to \infty$ as defined in Lemma~\ref{lemma:G-SVE_breakdown}. Then there exists an $N_0$ such that

@@

\xi\left(\hat{\Sigma}_{G}^{ij}, \tilde{\Sigma}^{ij} \right) = \Var\left(\hat{\Sigma}_{G}^{ij} - \tilde{\Sigma}^{ij} \right) + 2 \E\left[ \left(\hat{\Sigma}_{G}^{ij} -  \tilde{\Sigma}^{ij} \right) \left(\tilde{\Sigma}^{ij}  - \E \left( \tilde{\Sigma}^{ij} \right) \right) \right]\,.

@@

\cite{hannan:1970} has given the calculations for variance of $\tilde{\Sigma}$ as 
\begin{equation} \label{eq:hannan_var}
\dfrac{n}{b_n}\Var(\tilde{\Sigma}^{ij}) = \left[\Sigma^{ii}\Sigma^{jj} + \left(\Sigma^{ij} \right) \right]\int_{-\infty}^{\infty}w^2(x)dx + o(1)\,.
\end{equation}
Plugging (\ref{eq:hannan_var}) into variance of $\hat{\Sigma}_{G}$ gives the result of the theorem.
